Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with \pkg{ACSNMineR} and \pkg{RNaviCell} packages

### 2016-08-26 jss/Deveau.tex
Updated legends and figures for figures 1 & 2

\begin{figure}[h!]
	\centering
    \caption{Representation of the enriched modules (first six rows), with
    either Bonferroni correction or no correction. Grey tiles means that the
    data is not available for this module in this sample. P-values of low
    significance are in white, whereas p-values of high significance are
    represented in blue.}
    \includegraphics[width=0.8\textwidth]{figures/comparison_corrected_unc.pdf}
    \label{fig:heatm}

@@

\begin{figure}[h!]
	\centering
	\caption{Representation of the enriched modules (first six rows), with either Bonferroni correction (left) or no correction (right). The modules are on the X axis and the p-values are on the Y axis.  }
	\includegraphics[width=\textwidth]{figures/comparison_corrected_unc_bars.pdf}
	\label{fig:barp}

@@

\begin{tabular}{l c c c c}
\toprule
Module & Mod. size & Nb genes & pval & Cor. pval\\
\midrule
Apoptosis:AKT\_MTOR & 79 & 47 & 0.00 & 0.01 \\ 
CellCycle:E2F2\_TARGETS & 35 & 22 & 0.01 & 0.04 \\ 
CellCycle:E2F3\_TARGETS & 51 & 31 & 0.00 & 0.02 \\ 
CellCycle:E2F4\_TARGETS & 100 & 60 & 0.00 & 0.00 \\ 
DNA\_repair & 346 & 172 & 0.00 & 0.01 \\ 
DNA\_repair:CELL\_CYCLE & 82 & 49 & 0.00 & 0.01 \\ 
DNA\_repair:G1\_CC\_PHASE & 25 & 18 & 0.00 & 0.02 \\ 
DNA\_repair:S\_CC\_PHASE & 46 & 28 & 0.00 & 0.03 \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{figure}[h!]
	\centering
    \caption{Representation of the enriched modules (first six rows for each setting), with
    either Bonferroni correction or no correction. Grey tiles means that the
    data is not available for this module in this sample. P-values of low
    significance are in white, whereas p-values of high significance are
    represented in blue.}
    \includegraphics[width=0.8\textwidth]{figures/comparison_corrected_unc.pdf}
    \label{fig:heatm}

@@

\begin{figure}[h!]
	\centering
	\caption{Representation of the enriched modules (first six rows for each setting), with either Bonferroni correction (left) or no correction (right). The modules are on the X axis and the p-values are on the Y axis.  }
	\includegraphics[width=\textwidth]{figures/comparison_corrected_unc_bars.pdf}
	\label{fig:barp}

@@

\begin{tabular}{l c c c c}
\toprule
Module & Mod. size & Nb genes & pval & Cor. pval\\
\midrule
  Apoptosis:AKT\_MTOR & 79 & 47 & 0.00043 & 0.0068 \\ 
  CellCycle:E2F2\_TARGETS & 35 & 22 & 0.0055 & 0.043 \\ 
  CellCycle:E2F3\_TARGETS & 51 & 31 & 0.0023 & 0.025 \\ 
  CellCycle:E2F4\_TARGETS & 100 & 60 & $5.8 \times 10^{-5}$ & 0.0037 \\ 
  DNA\_repair & 346 & 172 & 0.00038 & 0.0068 \\ 
  DNA\_repair:CELL\_CYCLE & 82 & 49 & 0.00029 & 0.0068 \\ 
  DNA\_repair:G1\_CC\_PHASE & 25 & 18 & 0.0013 & 0.016 \\ 
  DNA\_repair:S\_CC\_PHASE & 46 & 28 & 0.0036 & 0.033 \\ 
\bottomrule
\end{tabular}
\end{table}
